---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# `CTUtemplate`

`CTUtemplate` is a package to create a template directory structure (and files) and also includes the CTUs annual safety report function.



## Installation

```{r, eval = FALSE}
remotes::install_github("CTU-Bern/CTUtemplate")
```


This may require `Sys.setenv(R_REMOTES_NO_ERRORS_FROM_WARNINGS="true")` if packages were built under a different R version to the one you are using.

## Usage

### Template director structure

Once installed, in RStudio, open a "new project in a new directory" and select "CTU project template". Options in the following window are used to create the folders and headers of R (and eventually STATA) files.


### Annual safety report

The `asr` function is used to fill out the Swiss Ethics Annual Safety Report template. It is intended that by passing a dataframe with the relevant information, plus a few other values, filling the template can be automated.

Assuming that all data variables are consistent with the defaults, the following might be used to fill out the report.

```{r, eval=FALSE}
asr(dataframe,
    trial_title = "Trial Name",
    protocol_number = "1",
    basec_number = "2153153",
    snctp_number = "3516135468",
    swissmedic_number = "kuis16153613",
    ec_name = "KEK Bern",
    product_name = "Drug name",
    sponsor_contact = "Mr Foo, University of Foo, Bar", 
    inst_name_address = "Mr Bar, University of Foo, Bar",
    n_centers_t = length(unique(alldata$site)),      # total number of sites
    n_centers_p = 15,                                # number of planned sites
    n_centers_c = length(unique(closedsites$site)),  # number of closed sites
    n_centers_o = length(unique(alldata$site)),      # number of open sites
    n_pat_t = 1000,                                  # total number of participants
    n_pat_e = length(unique(alldata$record_id)),     # enrolled participants
    n_pat_c = sum(all_data$eos_complete),            # complete participants
    n_pat_p = sum(all_data$eos_terminated),          # prematurely terminated participants
    period_from = min(dataframe$ic_date),            # assuming that the variable exists!
    period_to = Sys.Date()
    )
```

 






