---
knit: 
  bookdown::render_book:
    output_dir: ""
output: CTUtemplate::report_pdf
toc: true
lot: false
lof: false
params:
  author: "FirstName LastName"
  email: "FirstName.LastName@ctu.unibe.ch"
  job: "Senior Statistician"
  projnum: 1234
  projname: "Project X"
  version: "xx"
  reportname: "Report on Sample Size Calculation"
  dir: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval = FALSE, echo = FALSE}
# Run this ONCE MANUALLY to generate files required by the UNIBE latex template
CTUtemplate::use_ubreportclo(
  # THE SAME DIR AS THE Rmd FILE
  dir = params$dir, 
  # Personal info
  sign = params$author,
  email = params$email,
  job = params$job,
  # Project info
  projnum = params$projnum,
  projname = params$projname,
  # Report info
  version = params$version,
  reporttype = params$reportname
)
# 'ordinary' Rmd files would have this specified in the yaml header, but that 
#   doesnt work with the LaTeX template... hence, an additional file needs to be 
#   defined.
```

# Administrative Information {-}

----------------  -----------------
Project number    `r params$projnum`
Protocol version  V1
----------------  -----------------


\chapter{Study objective}

# Primary objective 

Describe study objective. The study objective will usually be defined according to:
* Patients: Which patients are included in the study?
* Interventions: Which are the intervention groups?
* Comparisons: Which are the control groups?
* Outcome: Which is the primary outcome?

# Primary outcome

Description of primary outcome, including:
*	Type of data (binary, ordinal, continuous, count, time-to-event)
*	Time point of assessment
*	In case of continuous outcomes, the measurement scale/units of measurements

# Hypothesis (if applicable)
*	Description of null and alternative hypothesis
*	Testing framework (e.g. superiority)


\chapter{Methods and assumptions}

*	Allocation ratio,
*	Type I and II error rate,
*	Effect measure, e.g. relative risk, difference in means
*	Minimal clinically relevant difference between the groups (or non-inferiority margin),
*	Assumptions about any further parameter that is used, e.g. standard deviation for continuous outcomes, baseline proportion/rate for binary/survival outcomes.
*	Any corrections for dropouts or withdrawals (if applicable),
*	Method or test used for the sample size calculation,
*	Statistics software used (unless standard test/method is used)

```{r, include=FALSE}
# do calculations here...
```


\chapter{Result of sample size calculation}
*	Result, e.g. a table
*	Wording of sample size calculation for the study proposal/protocol

